\documentclass[11pt]{article}
\usepackage{times,graphicx,epstopdf,fancyhdr,amsfonts,amsthm,amsmath,url,xspace,amssymb, listings, enumitem}
\usepackage[left=.75in,top=1in,right=1in,bottom=.75in]{geometry}
\usepackage{booktabs}
\usepackage[singlelinecheck=false]{caption}
\usepackage[nocenter]{qtree}
\pagestyle{fancy}
\lstloadaspects{keywordcomments}

\title{Midpoint DP Reflection}
\author{Stephen L. White}
\date{March 24, 2017}
%Comment out for single spacing
%\baselineskip 20pt

\lhead{Stephen L. White}
\chead{\textbf{Midpoint DP Reflection}}
\rhead{24 March 2017}
\lfoot{6.033}
\cfoot{}
\rfoot{\thepage}


\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headwidth}{\textwidth}
%\addtolength{\headwidth}{\marginparwidth}
%\addtolength{\headwidth}{\marginparsep}
\renewcommand{\footrulewidth}{0.4pt}
\begin{document}

\paragraph{Reflection:}

So far, the collaboration in our team has went smoothly. It seems evident that all of us have had collaboration experience before, whether at internships or in other classes. We began by meeting and digesting all of the available information, and breaking everything down into all of the headers which our DPPR should include. I stepped up and mostly handled this, as we we're having issues getting started / scheduling a time to meet. I figured that a blank white screen was intimidating, and that once we had it broken down into headers, it would be more managable. From there, we met as a group and divided content between each of the headers, and put some bullet points under each. We split up headers between the 3 of us. From there, we expanded each of the headers on our own time. Most of the design decisions were just made initially, then discussed through comments/revisions in the Google Doc. Design decisions have not yet caused major disagreements. Finally, after each of us completed our respective sections, we met again in person to read through the entire report. In this reading, we checked for consistency and cohesion. \\

So far, our group has not used stasis theory in our design project work.

\end{document}
